### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>53</td><td>13873</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>12624</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>12573</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>11463</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11325</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

>>>>

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>1</td><td>11750</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>11208</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11195</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>52</td><td>10907</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
